---
title: "PA1_template"
author: "Rick Yoo"
date: '2020 1 24 '
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

### 1. Loading and preprocessing the data
```{r}
DF <- read.csv('activity.csv')

library(tidyverse)
DF <- DF %>%
	select(date, interval, steps)
```

### 2. What is the mean total number of steps taken per day?  
```{r}
totalperday <- tapply(DF$steps, DF$date, sum, na.rm = TRUE)
barplot(totalperday, xlab='Date', ylab='Total # of steps')
```  

Mean = `r mean(totalperday)`  
Median = `r median(totalperday)`

### 3. What is the average daily activity pattern?
```{r}
dailyactivity <-  tapply(DF$steps, DF$interval, mean, na.rm=TRUE)
plot(names(dailyactivity), dailyactivity, type='l', xlab='interval', ylab='average steps')
```

Interval with maximum average = `` `r names(which(dailyactivity==max(dailyactivity)))` ``

### 4. Imputing missing values
```{r}
sum(is.na(DF))
newDF <- DF
for (i in 1:nrow(DF)) {
	if(is.na(newDF[i,]$steps)) {
		newDF[i,]$steps <- dailyactivity[[as.character(DF[i,]$interval)]]
	}
}
newtotalperday <- tapply(newDF$steps, newDF$date, sum, na.rm = TRUE)
barplot(newtotalperday, xlab='Date', ylab='Total # of steps')
```

new Mean = `r mean(newtotalperday)` ( > `r mean(totalperday)`)

new Median = `r median(newtotalperday)`( > `r median(totalperday)`)


### 5. Are there differences in activity patterns between weekdays and weekends?
```{r}
D <- newDF %>%
	mutate(dayend = ifelse(weekdays(as.Date(as.character(date), '%Y-%m-%d')) %in% c('토요일', '일요일'), 'weekend', 'weekday')) %>%
	mutate(dayend = as.factor(dayend)) %>%
	group_by(interval, dayend) %>%
	summarise(
		avg = mean(steps)
	)

ggplot(data = D) +
	geom_line(aes(interval, avg, col=dayend)) +
	facet_grid( dayend ~ . ) +
	ggtitle('Average steps across all weekday / weekend days')
```



